---
title: "cell_density"
author: "Bertille Smith"
date: "3/5/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(dplyr)
install.packages("tidyverse")

library("readxl")
library("ggplot2")
library("grid")
library("janitor")
library("dplyr")

source("../src/brewnalysis_functions_tosend.R")
source("../src/model_functions.R")
source("../src/rss_calculation_functions.R")
source("../src/estimate_parameters.R")

```
## Loading Brewery Data

```{r}
fermentation_data <- read_excel("../data/brewnalysis_test_data.xlsx") %>%
  janitor::clean_names() %>% na.omit() %>%
  dplyr::select(brand, batch_number,date,sample_time,dilution_factor,cell_count_1_live_cells,cell_count_1_squares_counted,cell_count_2_live_cells,cell_count_2_squares_counted,fermentation_day)

<<<<<<< HEAD:reports/script_cell_density_tosend2.Rmd
=======
if (("square_count" %in% colnames(fermentation_data)) & ("cell_count" %in% colnames(fermentation_data)) & ("dilution_factor" %in% colnames(fermentation_data))) {
  fermentation_data <- dplyr::mutate(fermentation_data,celldensity= (data_homog(fermentation_data))) 
} 
```


```{r}

#All the batches

if ("date" %in% colnames(fermentation_data)) {
>>>>>>> ec07672b5e065f0846076a2683e8212e4d9ec6c5:reports/cell_density.Rmd
cell_density=fermentation_data %>% 
  group_by(brand,batch_number) %>% 
  group_map(~ Cell_dens_func(.x))

  cell_density=bind_rows(cell_density)

cell_density=data.frame('brand' = fermentation_data$brand, 'batch_number' = fermentation_data$batch_number,'fermentation_day'= fermentation_data$fermentation_day,cell_density)

cell_dens_plot <- ggplot(cell_density, aes(x = Tvec, y = celldensity, group = interaction(brand, batch_number), color = brand)) +
  geom_point() +
  geom_line() +
  labs(title = "Cell density in wort according to fermentation time", x="Fermentation time (hours)",y="Cell density")+
  theme_classic()

<<<<<<< HEAD:reports/script_cell_density_tosend2.Rmd
# Loading Brewery Data : Single Batch

beer_a_b5 <- fermentation_data %>%
  dplyr::filter(brand == "beer_a", batch_number == 5)


=======
```

```{r}
#  Single Batch

#select the brand and batch number you want to see here
single_batch <- fermentation_data %>%
  dplyr::filter(brand == "ale1", batch_number == 1)
>>>>>>> ec07672b5e065f0846076a2683e8212e4d9ec6c5:reports/cell_density.Rmd

single_cell_density=Cell_dens_func(beer_a_b5)
single_cell_density=data.frame(single_cell_density,'brand' = beer_a_b5$brand, 'batch_number' = beer_a_b5$batch_number)


<<<<<<< HEAD:reports/script_cell_density_tosend2.Rmd
single_cell_dens_plot <-ggplot(single_cell_density, aes(x = Tvec, y = celldensity, group = interaction(brand, batch_number), color = brand)) +
=======
single_cell_dens_plot <-ggplot(single_cell_density, aes(x = Tvec, y = celldensity, group = interaction(brand, batch_number), color = interaction(brand))) +
>>>>>>> ec07672b5e065f0846076a2683e8212e4d9ec6c5:reports/cell_density.Rmd
  geom_point() +
  geom_line() +
  labs(title = "Cell density in wort according to fermentation time", x="Fermentation time (hours)",y="Cell density")+
  theme_classic()
```

<<<<<<< HEAD:reports/script_cell_density_tosend2.Rmd
#Plots

cell_dens_plot
=======
```{r}
#Plots
cell_dens_plot 
>>>>>>> ec07672b5e065f0846076a2683e8212e4d9ec6c5:reports/cell_density.Rmd
single_cell_dens_plot

#note : problem beer_c : I checked in the initial data and they made a mistake when they recorded the date (E69) : should we change it for 4/17/20 or delete this row ?
```

## ## Fitting the gamma model 

```{r}
gam_guess <- c(3,15)

<<<<<<< HEAD:reports/script_cell_density_tosend2.Rmd
tvec = cell_density$fermentation_day
Obs = cell_density$celldensity

=======
>>>>>>> ec07672b5e065f0846076a2683e8212e4d9ec6c5:reports/cell_density.Rmd
gam_fits <- cell_density %>%
  group_by(brand, batch_number) %>%
  summarize(gam_pars = est_gam_pars(gam_guess, Tvec, celldensity),
  samp_count = n())


<<<<<<< HEAD:reports/script_cell_density_tosend2.Rmd

gam_pred=gam_func(unlist(gam_pars),tvec)



#Condition of the data in the plot
Condition<-c("Gamma model data")
PVAL<-data.frame(tvec,gam_pred,Condition)

beer_a_b5$Condition_sample <-paste(beer_a_b5$brand,beer_a_b5$batch_number,sep="_b")

cell_density_gamma<-data.frame('Cell_density'=single_cell_density$cell_density,'Condition_sample'=single_cell_density$Condition_sample, 'Tvec'=single_cell_density$Tvec )%>%
  select(Tvec, celldensity,Condition_sample)


Sample_condition=c(cell_density_gamma$Condition_sample,PVAL$Condition)
cell_density_gamma_model=data.frame(cell_density_gamma,PVAL)%>%
  select(Tvec, celldensity,Condition_sample,gam_pred,Condition) %>%
  group_by(brand,batch_number)

#Plot

all_gamma_plot<- cell_density_gamma_model %>%
ggplot(aes(x=Tvec, y=celldensity, group=interaction(brand, batch_number,Sample_condition),color=Sample_condition))+ 
=======
plot_data <- gam_fits %>% left_join(cell_density) %>% rowwise() %>% mutate(gam_pred = gam_func(unlist(gam_pars[1:3]), Tvec)) 
  
  
  # %>% dplyr::select(brand, batch_number,Tvec, gam_pred, cell_density, gam_pars) %>%
 # pivot_longer(c(gravity, log_pred, gen_log_pred,exp_pred), names_to = "model_id", values_to = "specific_gravity")

###gam_pars=est_gam_pars(gam_guess,gam_fits[1],gam_fits[2]) 
####gam_pred=gam_func(unlist(gam_pars),tvec)

#gamma model

Condition_m<-c("Gamma model data")
Condition_e<-c("Empirical data")

cell_density_gamma<-data.frame('Tvec'=plot_data$Tvec,'celldensity'=plot_data$gam_pred,'brand'=plot_data$brand,'batch_number'=plot_data$batch_number,'Condition'=Condition_m)
cell_density_empirical=data.frame(cell_density,'Condition'= Condition_e)
cell_density_gamma_model=bind_rows(cell_density_gamma,cell_density_empirical)

#Plot

all_gamma_plot<- cell_density_gamma %>%
  dplyr::select(Tvec, celldensity,brand, batch_number)%>%
  ggplot(aes(x=Tvec, y=celldensity, group=interaction(brand, batch_number),color=brand))+ 
>>>>>>> ec07672b5e065f0846076a2683e8212e4d9ec6c5:reports/cell_density.Rmd
  geom_line() +
  geom_point()+
  labs(title = "Cell density in wort according to fermentation time", x="Fermentation time (hours)",y="Cell density")+
  theme_classic()

<<<<<<< HEAD:reports/script_cell_density_tosend2.Rmd
=======

single_gamma_plot_facet_grid<- cell_density_gamma_model %>%
  dplyr::filter(brand == "ale1", batch_number == 5) %>%
  ggplot(aes(x=Tvec, y=celldensity, group=interaction(brand, batch_number,Condition),color=Condition))+
  geom_point() +
  geom_line()+
  labs(title = "Cell density in wort according to fermentation time", x="Fermentation time (hours)",y="Cell density")+
  theme_classic() + facet_grid(~Condition)

>>>>>>> ec07672b5e065f0846076a2683e8212e4d9ec6c5:reports/cell_density.Rmd
single_gamma_plot<- cell_density_gamma_model %>%
  dplyr::filter(brand == "beer_d", batch_number == 2) %>%
  ggplot(aes(x=Tvec, y=celldensity, group=interaction(brand, batch_number,Sample_condition),color=Sample_condition))+
  geom_point() +
  geom_line()+
  labs(title = "Cell density in wort according to fermentation time", x="Fermentation time (hours)",y="Cell density")+
  theme_classic()


<<<<<<< HEAD:reports/script_cell_density_tosend2.Rmd

=======
single_gamma_plot_facet_grid
>>>>>>> ec07672b5e065f0846076a2683e8212e4d9ec6c5:reports/cell_density.Rmd
single_gamma_plot
all_gamma_plot
```
## ## Fitting the gamma + model 

```{r}
gam_a_guess <- c(1,3,15)
<<<<<<< HEAD:reports/script_cell_density_tosend2.Rmd
tvec_a = cell_density$Tvec
Obs_a = cell_density$celldensity
=======

>>>>>>> ec07672b5e065f0846076a2683e8212e4d9ec6c5:reports/cell_density.Rmd

gam_a_fits <- cell_density %>%
  group_by(brand, batch_number) %>%
  summarize(gam_a_pars = est_gam_a_pars(gam_a_guess, Tvec, celldensity),
  samp_count = n())

<<<<<<< HEAD:reports/script_cell_density_tosend2.Rmd

#gam_a_pars= est_gam_a_pars(gamAPar,gam_a_rss,tvec_plus,gamAPred)

gam_a_pred=gam_a_func(gam_a_pars,tvec_a)

#Condition of the data in the plot

Condition_a<-c("Gamma + model data")
PVAL_a<-data.frame(tvec_a,gam_a_pred,Condition_a)


beer_a_b5$Condition_sample <-paste(beer_a_b5$brand,beer_a_b5$batch_number,sep="_b")
cell_density_gamma_a=data.frame(cell_density,'Condition_sample'=beer_a_b5$Condition_sample )%>%
  select(Tvec, celldensity,Condition_sample)

=======
plot_data_a <- gam_a_fits %>% left_join(cell_density) %>% rowwise() %>% mutate(gam_a_pred = gam_a_func(unlist(gam_a_pars[1:4]), Tvec)) 

#gam_a_pars= est_gam_a_pars(gam_a_guess,tvec_a,Obs_a)
#gam_a_pred=gam_a_func(unlist(gam_a_pars),tvec_a)

#gamma + model
Condition_m_a<-c("Gamma + model data")
cell_density_gamma_a<-data.frame('Tvec'=plot_data_a$Tvec,'celldensity'=plot_data_a$gam_a_pred,'brand'=plot_data_a$brand,'batch_number'=plot_data_a$batch_number,'Condition'=Condition_m_a)
cell_density_empirical=data.frame(cell_density,'Condition'= Condition_e)
cell_density_gamma_a_model=bind_rows(cell_density_gamma_a,cell_density_empirical)
>>>>>>> ec07672b5e065f0846076a2683e8212e4d9ec6c5:reports/cell_density.Rmd

Sample_condition_a=c(cell_density_gamma_a$Condition_sample,PVAL_a$Condition_a)
cell_density_gamma_a_model=data.frame(cell_density_gamma_a,PVAL_a)%>%
  select(Tvec, celldensity,Condition_sample,Pval_a,Condition_a)


<<<<<<< HEAD:reports/script_cell_density_tosend2.Rmd
all_gamma_a_plot<- cell_density_gamma_a_model %>%
ggplot(aes(x=Tvec, y=celldensity, group=interaction(brand, batch_number,Sample_condition_a),color=Sample_condition_a))+ 
=======
#Plot
all_gamma_a_plot<- cell_density_gamma_a %>%
dplyr::select(Tvec, celldensity,brand, batch_number)%>%
ggplot(aes(x=Tvec, y=celldensity, group=interaction(brand, batch_number),color=brand))+ 
>>>>>>> ec07672b5e065f0846076a2683e8212e4d9ec6c5:reports/cell_density.Rmd
  geom_line() +
  geom_point()+
  labs(title = "Cell density in wort according to fermentation time", x="Fermentation time (hours)",y="Cell density")+
  theme_classic()

<<<<<<< HEAD:reports/script_cell_density_tosend2.Rmd
=======
single_gamma_a_plot_facet_grid<- cell_density_gamma_a_model %>%
  dplyr::filter(brand == "ale1", batch_number == 3) %>%
  ggplot(aes(x=Tvec, y=celldensity, group=interaction(brand, batch_number,Condition),color=Condition))+
  geom_point() +
  geom_line()+
  labs(title = "Cell density in wort according to fermentation time", x="Fermentation time (hours)",y="Cell density")+
  theme_classic()+ facet_grid(~Condition)

>>>>>>> ec07672b5e065f0846076a2683e8212e4d9ec6c5:reports/cell_density.Rmd
single_gamma_a_plot<- cell_density_gamma_a_model %>%
  dplyr::filter(brand == "beer_d", batch_number == 2) %>%
  ggplot(aes(x=Tvec, y=celldensity, group=interaction(brand, batch_number,Sample_condition_a),color=Sample_condition_a))+
  geom_point() +
  geom_line()+
  labs(title = "Cell density in wort according to fermentation time", x="Fermentation time (hours)",y="Cell density")+
  theme_classic()

<<<<<<< HEAD:reports/script_cell_density_tosend2.Rmd
=======
single_gamma_a_plot_facet_grid
>>>>>>> ec07672b5e065f0846076a2683e8212e4d9ec6c5:reports/cell_density.Rmd
single_gamma_a_plot
all_gamma_a_plot
```
## ## Cell density and models common plot
```{r}
<<<<<<< HEAD:reports/script_cell_density_tosend2.Rmd
cell_density_gamma_a_model%>%
  select(Pval_a,Condition_a)
cell_density_models=data.frame(cell_density_gamma_model,cell_density_gamma_a_model)%>%
  select(Tvec,celldensity, Condition_sample,Pval,Condition,Pval_a,Condition_a)
cell_density_common

cell_density_common_plot=ggplot(data=cell_density_common,aes(x=Tvec))+geom_line(aes(y=celldensity,colour = factor(Condition_sample)))+geom_point(aes(y=celldensity,colour = factor(Condition_sample)))+geom_line(aes(y=Pval,colour = factor(Condition)))+geom_point(aes(y=Pval,colour = factor(Condition)))+geom_line(aes(y=Pval_a,colour = factor(Condition_a)))+geom_point(aes(y=Pval_a,colour = factor(Condition_a)))+labs(title = "Cell density in wort according to fermentation time", x="Fermentation time (hours)",y="Cell density")
=======
cell_density_common_model=bind_rows(cell_density_gamma_a,cell_density_empirical,cell_density_gamma)
cell_density_common_plot<- cell_density_common_model %>%
  dplyr::filter(brand == "ale1", batch_number == 2) %>%
  ggplot(aes(x=Tvec, y=celldensity, group=interaction(brand, batch_number,Condition),color=Condition))+
  geom_point() +
  geom_line()+
  labs(title = "Cell density in wort according to fermentation time", x="Fermentation time (hours)",y="Cell density")+
  theme_classic()

cell_density_common_plot_facet_grid<- cell_density_common_model %>%
  dplyr::filter(brand == "ale1", batch_number == 2) %>%
  ggplot(aes(x=Tvec, y=celldensity, group=interaction(brand, batch_number,Condition),color=Condition))+
  geom_point() +
  geom_line()+
  labs(title = "Cell density in wort according to fermentation time", x="Fermentation time (hours)",y="Cell density")+
  theme_classic() + facet_grid(~Condition)
>>>>>>> ec07672b5e065f0846076a2683e8212e4d9ec6c5:reports/cell_density.Rmd

cell_density_common_plot_facet_grid
cell_density_common_plot
```
